A seamless, client-centric programming model for type safe web applications

### 2014-05-02 paper.tex
Remove split infinitive. Apparently, grammar can be controversial.
Update info on where to obtain Haste.

This is the final part of our program; we set up an event handler to clear the
input box and send its contents off to the server whenever the user hits return
(character code 13) while the input box has focus. Finally, all that is left
is to actually launch our application.

@@

The implementation described here is a slight simplification of our
implementation, removing some performance enhancements and error handling
clutter in the interest of clarity. The complete implementation is available
for download, together with the Haste compiler, from our source repository at
\lstinline!http://ekblad.cc/haste!.

>>>>

This is the final part of our program; we set up an event handler to clear the
input box and send its contents off to the server whenever the user hits return
(character code 13) while the input box has focus. Finally, all that is left
is to launch our application.

@@

The implementation described here is a slight simplification of our
implementation, removing some performance enhancements and error handling
clutter in the interest of clarity. The complete implementation is available
for download, together with the Haste compiler, from Hackage as well as from
our website at \lstinline!http://haste-lang.org!.
